### 2016-07-17 image_paper3/text_files/image_texts/col3byall.tex
fig.s and table corrections

\begin{figure*}
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
        \label{fig: col3and11_dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
        \label{fig: col3and12_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
        \label{fig: col3and13_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
        \label{fig: col3and14_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
        \label{fig: col3and15_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
        \label{fig: col3and16_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
        \label{fig: col3and17_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
        \label{fig: col3and18_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
        \label{fig: col3and19_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
        \label{fig: col3and20_dist}
    \end{subfigure}        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
        \label{fig: col3and21_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
        \label{fig: col3and22_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
        \label{fig: col3and23_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
        \label{fig: col3and24_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
        \label{fig: col3and25_dist}
    \end{subfigure}
    \caption{Results from increasing dimension of input data from 11 to 25}
    \label{fig: inc_D_col3s}
\end{figure*}

>>>>

\begin{figure}
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and11.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: only_pahs} and \halpha} 
        \label{fig: col3and11_dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and12.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and11_dist} and \oiii} 
        \label{fig: col3and12_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and13.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and12_dist} and \sii} 
        \label{fig: col3and13_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and14.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and13_dist} and IRAC~5.7~$\mu$m emission} 
        \label{fig: col3and14_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and15.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and14_dist} and PACS~100~$\mu$m emission} 
        \label{fig: col3and15_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and16.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and15_dist} and SPIRE~250~$\mu$m emission} 
        \label{fig: col3and16_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and17.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and16_dist} and SPIRE~350~$\mu$m emission} 
        \label{fig: col3and17_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and18.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and17_dist} and SPIRE~500~$\mu$m emission} 
        \label{fig: col3and18_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and19.png}
         \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and18_dist} and L$_{\mathrm{ Dust}}$} 
        \label{fig: col3and19_dist}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and20.png}
          \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and M$_{\mathrm{ Dust}}$} 
        \label{fig: col3and20_dist}
    \end{subfigure}        \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and21.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and20_dist} and SFR(FUV\ +\ 24\ $\mu$m)} 
        \label{fig: col3and21_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and22.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and21_dist} and M$_{\mathrm{ Stars}}$} 
        \label{fig: col3and22_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and23.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and22_dist} and L$_{\mathrm{ TIR}}$} 
        \label{fig: col3and23_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and24.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and23_dist} and M$_{\mathrm{ Total\ gas}}$.} 
        \label{fig: col3and24_dist}
    \end{subfigure}
            \hfill
    \begin{subfigure}[b]{0.25\textwidth}
        \centering
        \includegraphics[width=52mm, height=32mm ]{../../images0.01/M31/2D/diff_dimension/combine_2D_data_between_cols3and25.png}
        \captionsetup{font=tiny}
        \caption{Input data: data from Fig.~\ref{fig: col3and19_dist} and RHI.} 
        \label{fig: col3and25_dist}
    \end{subfigure}
    \caption[Increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually]{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually. The order of input data is the same as the order of data in Fig.~\ref{fig: cor_cluster1}.} 
    \label{fig: inc_D_col3s}
\end{figure}

### 2016-07-17 version0.0/appendixa_2.tex
fig.s and table corrections

\chapter{SFR from H$\alpha$ plus 24 \um: procedure and result}
\pagestyle{plain}
\label{app:halpha}
\myappendices{
As mentioned in Section~\ref{sec:data}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create one of our SFR maps. These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands and were observed between August 2000 and September 2002; we obtained them  from the NOAO Science Archive. Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted images, and finally correcting for the flux contribution to the \halpha filter from the \nii\ 6583~\AA\ line.

The Nearby Galaxies survey $R$-band images were used to remove the stellar emission from H$\alpha$ using the scaling factor between fluxes in these two band passes determined by \citet{Azimlu11}. They estimated continuum emission in each H$\alpha$ image, using photometric measurements in both \halpha and R-band images, and determined the scaling factor. These images were observed from a ground-based telescope over two years' time. Consequently, there is a non-negligible sky contribution in the background which must be estimated and removed from each image in both bands. Unfortunately, there is no nearby `blank-sky' image taken with the same instrument available from which to measure the sky contribution, which makes the removal of background emission even harder. The only remaining choice is to subtract the local background for each region. However, subtracting local backgrounds from each image will result in a non-smooth background in the final mosaic image.

\begin{figure*}
\centering
\includegraphics[width=164mm]{../image_paper1/halpha.pdf}
\caption{Mosaic created using the Montage programme from six fields of H$\alpha$ emission images of M31 from \citet{Massey07}. The resulting image from Montage was continuum-subtracted and masked for all point sources. The centre of the galaxy was masked out due to saturation of data in the continuum $R$-band image.}
\label{fig:halpha}
\end{figure*}

To create the final mosaic, first we removed the background from each region in both the \halpha and $R$-band images. The second step was to subtract the continuum from the \halpha images. Since both \halpha and $R$-band images were aligned on the same coordinate grid, for each field, the R-band image multiplied by the scaling factor was subtracted from each corresponding \halpha image. At the end, we masked out all the foreground and saturated regions which include a 10\arcmin $\times$ 10\arcmin region in the centre of the galaxy. To account for the flux contribution of the [N II] emission we used the flux ratio ${\mathrm \nii}/{\mathrm H}\alpha = 0.54$ from \citet{Kennicutt08}, and subtracted it from the \halpha map. We created the final mosaic image, Figure~\ref{fig:halpha}, using the Montage program \citep{Berriman08}.

Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}. In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}. The fitting results using SFR(\halpha $+$ 24~$\mu$m) are more or less the same as the other two SFR tracers. The main reason for this difference is the missing data in the centre of the galaxy and the lack of smooth background in the \halpha data. Thus we did not include the SFR(\halpha $+$ 24~$\mu$m) in our final analysis.

\newpage
\section{More results from the fitting of the extended Schmidt law}
\label{app:es,figs}
Section~\ref{sec: sfl} discusses testing the extended Schmidt law and shows results for one SFR/gas tracer combination. Here we present the plots for the remaining SFR/gas tracer combinations.

>>>>

\chapter{More results from the fitting of the extended Schmidt law}
\pagestyle{plain}
\label{app:es,figs}
\myappendices{
Section~\ref{sec: sfl} discusses testing the extended Schmidt law and shows results for one SFR/gas tracer combination. Here we present the plots for the remaining SFR/gas tracer combinations.

### 2016-07-17 version0.0/asli.tex
fig.s and table corrections

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage{hyperref} %comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{chapterbib}
\makeatletter
\numberwithin{figure}{chapter}
\newenvironment{acknowledgements}%
{\clearemptydoublepage
 \begin{center}
  \section*{Acknowledgements}
 \end{center}
 \begingroup
}{\newpage\endgroup}

@@

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
%\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic Star Formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
The work presented in this thesis has greatly benefited from advice by my supervisor Dr. Pauline Barmby and collaborators: Dr. Sofia Lianue, Dr. Hossein Teimoorinia, and Dr. Els Peeters. Although I led the projects, performed the analysis and wrote the manuscripts, their suggestions and feedback on the analyses and manuscripts were greatly helpful.

{\bf Chapter 2}: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in the Monthly Notices of the Royal Astronomical Society, Volume 456, Issue 4, 2016.

{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future.

{\bf Chapter 4}: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to The Monthly Notices of The Royal Astronomical Society.
}

@@

\emph{To my parents, my sisters,}

\emph{\& Matin,}

\emph{for their unconditional love and support.}

@@

\include{intro0.0}
\include{paper1}
\include{paper3}
\include{paper2}
\include{summary}

@@

% %Appendices.
\begin{appendices}
\include{appendixa}
\include{appendixb}
\include{appendixc}
\end{appendices}

>>>>

\documentclass[12pt,twoside]{report}
%% Decomment next line to use PostScript fonts
%%\UsePackage{times}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                    %%
%%                    ***   I M P O R T A N T   ***                   %%
%%                                                                    %%
%% Fill in the following fields with the required information:        %%
%%  - \department{...}  name of the graduate department               %%
%%  - \degree{...}      name of the degree obtained                   %%
%%  - \author{...}      name of the author                            %%
%%  - \title{...}       title of the thesis                           %%
%%  - \gyear{...}       year of graduation                            %%
%%  - \super{...}    supervisor
%%  - \firstname, \middlename, \lastname... there is additional documentation by the actual fields, so I'll leave it at that
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{appendix}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[byname]{smartref}
\usepackage{hyperref}%comment out for hardcopy
\usepackage{txfonts}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{times}
\usepackage{float}
%\usepackage{caption}
\usepackage[font=small,labelfont=bf]{caption}
\DeclareCaptionFont{tiny}{\tiny}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{import}
\usepackage{ae,aecompl}
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage[flushleft]{threeparttable}
\usepackage{pgffor}
\usepackage{chapterbib}
\usepackage{adjustbox}

\makeatletter
\numberwithin{figure}{chapter}
\newenvironment{acknowledgements}%
{\clearemptydoublepage
 \begin{center}
  \section*{Acknowledgements}
 \end{center}
 \begingroup
}{\newpage\endgroup}

@@

\newcommand\acknowlege[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Acknowledgements\normalsize\\\indent\\#1\newpage
  \fi
}
\newcommand\dedications[1]{%
  \edef\@tempa{#1}%
  \def\@tempb{}%
  \ifx\@tempa\@tempb
	\else \newpage \Large Dedication\normalsize\\\indent\\#1\newpage
  \fi
}
%\renewcommand{\appendixtocname}{\Huge \textbf{List of Appendices} \normalsize}
\newcommand{\blank}{\hspace{-2mm}}
\newcommand{\super}{Dr. P. M. Barmby} %supervisor
\newcommand{\sco}{Dr. E. Peeters}  %member of supervisory committee
\newcommand{\sct}{Dr. G. Osinski}  %other member of supervisory committee (lbin)
\newcommand{\examo}{Dr. R. Abraham}  %examining committee (up to four, if less leave blank)
\newcommand{\examt}{Dr. M. Daley}
\newcommand{\examth}{Dr. S. C. Gallagher}
\newcommand{\examf}{Dr. P. Wiegert}
\newcommand{\department}{Physics and Astronomy}
\newcommand{\degree}{Doctor of Philosophy}
\newcommand{\firstname}{Sahar}
%\newcommand{\middlename}{}
\newcommand{\lastname}{Rahmani}
%\renewcommand{\author}[1]{\ifx\empty#1\else\gdef\@author{#1}\fi} 
\newcommand{\authorname}{{\firstname} {\middlename} {\lastname}}
\newcommand{\titl}{What governs star formation in galaxies? A modern statistical approach}
\newcommand{\spinetitle}{Extragalactic Star Formation}%only if the above is more than 60 characters
\newcommand{\thesisformat}{Integrated Article} %or Integrated Article
\newcommand{\gyear}{\number\year}
\newcommand{\makecoauthor}{
%Type information about coauthorship here/
The work presented in this thesis has greatly benefited from advice by my supervisor Dr. Pauline Barmby and collaborators: Dr. Sofia Lianou, Dr. Hossein Teimoorinia, and Dr. Els Peeters. Although I led the projects, performed the analysis and wrote the manuscripts, their suggestions and feedback on the analyses and manuscripts were priceless.

{\bf Chapter 2}: Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation, has been published in {\em Monthly Notices of the Royal Astronomical Society}, Volume 456, Issue 4, 2016.

{\bf Chapter 3}: Data Mining in Nearby Galaxies, will be submitted in the near future. %TBD: change this if you change the title

{\bf Chapter 4}: Clustering galaxy spectra at $0.5<z<1$: an unsupervised approach, has been submitted to {\em Monthly Notices of the Royal Astronomical Society}.
}

@@

To my parents, my sisters, \& Matin, for their unconditional love and support.

@@

% \include{intro0.01}
 \include{paper1}
%\include{paper3}
%\include{paper2}
% \include{summary}

@@

% %Appendices.
% \begin{appendices}
% \include{appendixa}
% \include{appendixa_2}
% \include{appendixb}
% \include{appendixc}
% \end{appendices}

### 2016-07-17 version0.0/intro0.0.tex
fig.s and table corrections

The most well-known scaling law is the relation between the surface densities of the star formation rate and the gas mass, known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98a}. 
The K-S law and similar empirical laws have been tested on local and high-redshift galaxies with various morphological types, on local and global scales and different ISM types~\citep[e.g][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.
Despite all these studies, many questions about star formation laws still remain unanswered; the limitations of star formation laws are yet undetermined and there is no definitive answer on whether there is any universal star formation law.
Their dependence on physical properties of galaxies is nontrivial and sometimes differs by type of star forming regions.
Although a relation between star formation and gas is well established, the details of this relation are not clear:
different types of gas affect SFR in different ways, and variations in metallicity alter the effects.
There is no fully sampled and universal IMF,
in fact there are many debates on whether the IMF is universal or not.
The influence of evolved stars and distance of star forming regions from centre of galaxies on SFR has been mentioned in studies but not fully investigated.
Besides studying the impact of the above-mentioned properties of galaxies on SFR, searching for other relations between properties of galaxies and their star forming regions continues.

>>>>

The most well-known scaling law is the relation between the surface densities of the star formation rate and the gas mass, known as the Kennicutt-Schmidt (KS) law~\citep{Schmidt59, Kennicutt98b}. 
The K-S law and similar empirical laws have been tested on local and high-redshift galaxies with various morphological types, on local and global scales and different ISM types~\citep[e.g][]{Kennicutt08,Bigiel08,Genzel10,Gnedin10,Shi11}.
Despite all these studies, many questions about star formation laws still remain unanswered; the limitations of star formation laws are yet undetermined and there is no definitive answer on whether there is any universal star formation law.
Their dependence on physical properties of galaxies is nontrivial and sometimes differs by type of star forming regions.
Although a relation between star formation and gas is well established, the details of this relation are not clear:
different types of gas affect SFR in different ways, and variations in metallicity alter the effects.
There is no fully sampled and universal IMF,
in fact there are many debates on whether the IMF is universal or not.
The influence of evolved stars and distance of star forming regions from centre of galaxies on SFR has been mentioned in studies but not fully investigated.
Besides studying the impact of the above-mentioned properties of galaxies on SFR, searching for other relations between properties of galaxies and their star forming regions continues.
